---
title: "Introduction to shinyrepro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to shinyrepro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyrepro)
```

## Using shinyrepro

There is a single exported function, `repro`, that will take a reactive object, and returns a character vector
of the code required to run outside of Shiny to re-create the specified reactive.

## Limitations

### Anonymous Functions

Currently it is hard to check the contents of anonymous functions for inputs and/or reactive objects, such
as functions used in the `apply` family functions or `purrr::map`. The workaround for this is to have
them as named arguments, therefore they are sent to the anonymous function as updated in shinyrepro.

```r
# Bad
purrr::map_dbl(1:10, \(x) x * input$mult)

# Good
purrr::map_dbl(1:10, mult = input$mult, \(x, mult) x * mult)
```
